GO

### 2019-12-12 analysis/12_GO.Rmd
markdown format

kable(hyp)  
kable(pit)  
kable(gon)  
```

>>>>

kable(hyp,  format = "markdown")  
# top GO therms for hyp:
# endocrine process, regulation of hormone levels,
# signal release # hormone secretion, # system process
# hormone transport, cell-cell signaling

kable(pit,  format = "markdown")
# endocrine process, mating behavior, system process,
# reproductive behavior, mating, regulation of blood pressure
# signal release, regulation of hormone levels

kable(gon)  
# endocrine process, regulation of blood pressure
# blood circutation, circulatory system
```
